bounding_box_preprocesing

### 2021-05-25 preprocessing/step4_create_bounding_box_summaries.Rmd
minor updates to bounding box summaries csript

   # if data wasn't normalized -- some (but not all!) Y videos
   if (this_vid_data$child_id[1]=='Y' &  max(this_vid_data$height, na.rm=TRUE)>1) {
     this_vid_data <- this_vid_data %>% 
        mutate(top = top/y_max, height = height/y_max, left = left/x_max, width = width/x_max)
   }

   this_vid <- this_vid_data %>%
      filter(!is.na(height)) %>%
      filter(mean_confidence > 0) %>% # sanity
      mutate(area = height * width) %>%
      group_by(label, child_id, vid_name) %>%
      summarize(num_detect = length(height), avg_area = median(area), avg_height = median(height), avg_width = median(width), avg_left = median(left), avg_top = median(top))

   empty_vid = (length(this_vid$num_detect)==0)
   if (empty_vid) {
     print(vid_file)
    }

   if (vid_index == 1 ){
     all_vid_bbs <- this_vid
   }
   else if (vid_index > 1 && empty_vid==FALSE) {
   all_vid_bbs <- all_vid_bbs %>%
     full_join(this_vid)
   }
}
}
```

```{r}
all_vid_bbs <- all_vid_bbs %>%
  left_join(age_info) %>%
  rowwise() %>%
  mutate(date_filmed = lubridate::ymd(str_split_fixed(vid_name,"_",4)[[2]])) %>%
  mutate(age_days = as.numeric(difftime(date_filmed,bday)) )

save(all_vid_bbs,file=here::here('data/preprocessed_data_2021/bounding_box_summaries_all.RData'))

>>>>

   # # if data wasn't normalized -- some (but not all!) Y videos
   # if (this_vid_data$child_id[1]=='Y' &  max(this_vid_data$height, na.rm=TRUE)>1) {
   #   this_vid_data <- this_vid_data %>% 
   #      mutate(top = top/y_max, height = height/y_max, left = left/x_max, width = width/x_max)
   # }

   # this_vid <- this_vid_data %>%
   #    filter(!is.na(height)) %>%
   #    filter(mean_confidence > 0) %>% # sanity
   #    mutate(area = height * width) %>%
   #    group_by(label, child_id, vid_name) %>%
   #    summarize(num_detect = length(height), avg_area = median(area), avg_height = median(height), avg_width = median(width), avg_left = median(left), avg_top = median(top))

   this_vid_faces <- this_vid_data %>%
      filter(!is.na(height)) %>%
      filter(label=='face') %>%
      filter(mean_confidence > 0)

   empty_vid=FALSE
   # empty_vid = (length(this_vid_data$num_detect)==0)
   # if (empty_vid) {
   #   print(vid_file)
   #  }

   if (vid_index == 1 ){
     # all_vid_bbs <- this_vid
     all_faces <- this_vid_faces
   }
   else if (vid_index > 1 && empty_vid==FALSE) {
   # all_vid_bbs <- all_vid_bbs %>%
   #   full_join(this_vid)

   all_faces <- all_faces %>%
      full_join(this_vid_faces)
   }
}
}
```

```{r}
# all_vid_bbs <- all_vid_bbs %>%
#   left_join(age_info) %>%
#   rowwise() %>%
#   mutate(date_filmed = lubridate::ymd(str_split_fixed(vid_name,"_",4)[[2]])) %>%
#   mutate(age_days = as.numeric(difftime(date_filmed,bday)) )
# 
# save(all_vid_bbs,file=here::here('data/preprocessed_data_2021/bounding_box_summaries_all.RData'))

all_faces <- all_faces %>%
  left_join(age_info) %>%
  rowwise() %>%
  mutate(date_filmed = lubridate::ymd(str_split_fixed(vid_name,"_",4)[[2]])) %>%
  mutate(age_days = as.numeric(difftime(date_filmed,bday)) )

 save(all_vid_bbs,file=here::here('data/preprocessed_data_2021/all_faces_summary.RData'))
